---
title: "Friends Viewership Report"
author: "yifan yang474665"
date: "2026-05-08"
format:
  html:
    theme: cosmo
    toc: true
---

## Introduction

*Friends* is an American television sitcom created by David Crane and Marta Kauffman. 
It aired on NBC from September 22, 1994 to May 6, 2004, lasting 10 seasons and 236 episodes. 
The show follows six friends living in New York City: Rachel, Monica, Phoebe, Joey, Chandler, and Ross.
*Friends* became one of the most popular TV shows in history and remains widely watched today.

![Friends Logo](Friends_logo.svg){width=400}

## Viewership Data

```{r}
#| echo: false
#| message: false
#| warning: false

library(tidyverse)
library(scales)
library(knitr)

# Data from Wikipedia
friends_data <- data.frame(
  Season = 1:10,
  Viewers = c(24.3, 30.0, 24.9, 24.0, 23.5, 20.7, 20.2, 24.5, 21.8, 22.8)
)
```

### Summary Table

```{r}
#| echo: false
friends_data |>
  mutate(Viewers = paste0(Viewers, "M")) |>
  rename("Season" = Season, "Avg. Viewers (millions)" = Viewers) |>
  kable()
```

## Viewership Over Time

```{r}
#| echo: false
ggplot(friends_data, aes(x = Season, y = Viewers)) +
  geom_line(color = "#4A90D9", linewidth = 1.2) +
  geom_point(color = "#4A90D9", size = 3) +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Friends — Average Viewers per Season",
    x = "Season",
    y = "Viewers (millions)"
  ) +
  theme_minimal()
```

## Season-to-Season Changes

```{r}
#| echo: false
friends_data <- friends_data |>
  mutate(Change = Viewers - lag(Viewers))

ggplot(friends_data[-1, ], aes(x = Season, y = Change, fill = Change > 0)) +
  geom_col() +
  scale_fill_manual(values = c("TRUE" = "#2ECC71", "FALSE" = "#E74C3C"),
                    labels = c("TRUE" = "Increase", "FALSE" = "Decrease"),
                    name = "") +
  scale_x_continuous(breaks = 2:10) +
  labs(
    title = "Friends — Season-to-Season Change in Viewership",
    x = "Season",
    y = "Change in Viewers (millions)"
  ) +
  theme_minimal()
```

## Analysis

```{r}
#| echo: false
max_s   <- friends_data$Season[which.max(friends_data$Viewers)]
max_v   <- max(friends_data$Viewers)
min_s   <- friends_data$Season[which.min(friends_data$Viewers)]
min_v   <- min(friends_data$Viewers)
drop_s2_s7 <- friends_data$Viewers[2] - friends_data$Viewers[7]
```

*Friends* reached its peak viewership in Season `r max_s` with `r max_v` million average viewers. 
The show experienced a notable decline from Season 2 to Season 7, dropping by `r drop_s2_s7` million viewers. 
The lowest average viewership was recorded in Season `r min_s` with `r min_v` million viewers.
Interestingly, Season 8 saw a recovery, climbing back to `r friends_data$Viewers[8]` million viewers.
